The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-21 analysis/paper/paper.qmd
Update other top words functions

# The top 10 words that are the most common in each topic
emu_theses_top_terms <- get_top_words_per_topic(emu_theses_topics, 20, "topic", "beta")

emu_theses_top_terms |> 
  mutate(term = reorder(term, beta)) |> 
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()

@@

```{r}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_theses_words, 
                           top_n = 3, 
                           title_col = "title", 
                           word_col = "word")
```

```{r}
# Which are the top n most frequently used words in all theses`?
get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 5, 
                         word_col = "word")
```

```{r}
# Which are the top n most frequently used words in all theses`?
emu_theses_top_20 <- get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 20, 
                         word_col = "word")
```

>>>>

# The top 10 words that are the most common in each topic
emu_theses_top_terms <- get_top_words_per_topic(emu_theses_topics, 20)

emu_theses_top_terms |> 
  ggplot(aes(reorder(term, beta), beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()

@@

```{r}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_theses_words, 
                           top_n = 3)
```

```{r}
# Which are the top n most frequently used words in all theses`?
get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 5)
```

```{r}
# Which are the top n most frequently used words in all theses`?
get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 20)
```
